\documentclass[letterpaper,10pt]{article}

\usepackage{resume}
\usepackage[pdftex,
            bookmarks=true,
            unicode=true,
            pdfauthor={Evan Purkhiser},
            pdftitle={Evan Purkhiser's Resume}]{hyperref}

\begin{document}

\section{Evan Purkhiser}

\hfill San Francisco, California --
\href{mailto:evanpurkhiser@gmail.com}{evanpurkhiser@gmail.com} --
\href{https://evanpurkhiser.com}{evanpurkhiser.com}

\subsection{Qualifications}

BS - Computer Science 2013\\
Akron, Ohio - The University of Akron

\begin{skills}
\item[Environments]
  GNU/Linux, BSD/macOS, AWS
\item[Languages]
  Golang, Python, ES7 (react, redux, node), HTML5, CSS3, SASS, SQL,
  Ruby, PHP, C++, Shell
\item[Software]
  Bash, Git, SVN, Mercurial, VIM, GNU Coreutils, Vagrant, Berkshelf,
  Chef-Solo, Ansible, Salt, Apache, nginx, MySQL, Redis, Bower, Browserify,
  Webpack, npm, PHP Composer, golang glide, jq
\end{skills}

\subsection{Experience}

\subsubsection{Crunchyroll / VRV}
\hfill Senior Software Engineer --- \emph{May 2015 - Present}

\begin{itemize}
\tightlist{}
\item
  Designed and developed high performance APIs using golang to serve
  video content metadata. Applied the HATEOAS constraint of REST to provide
  flexibility during rapid API design changes.
\item
  Full stack implementation of a `content partner' portal for content
  management. Developed using React-Redux alongside modern web technologies,
  with special attention given to the `look and feel' of the application.
\item
  Maintained production micro-services deployed in AWS\@. Used tooling such as
  NewRelic to investigate and quickly determine resolutions for live issues.
  This included an internal video ingestion system of which a deep
  understanding of many moving parts (encoding, metadata parsing, image
  conversion) was critical in resolving issues.
\item
  Architected and developed secure authentication mechanisms for a novel
  dual subscription linking system using the OAuth 1.0 protocol for the
  accounts API driving the \emph{VRV} product.
\item
  Improved developer experience by reworking an internal developer VM to be
  powered by Vagrant, including configuration management using salt.
\end{itemize}

\subsubsection{Crunchyroll}
\hfill Software Engineer --- \emph{August 2014 - May 2015}

\begin{itemize}
\tightlist{}
\item
  Spearheaded the divorce of a deeply integrated client frontend and monolith
  backend into a cleanly separated API consuming client using a modern PHP
  Symfony stack for the \emph{KDrama} product.
\item
  Promoted quality coding standards, git best practices, review best
  practices, automated style lint tooling, and improved developer environment
  tooling throughout the organization for a high quality developer
  experience.
\item
  Took initiative to update and own project library dependency versions.
  Various projects were updated to the newest Symfony2 framework along with
  other libraries, providing for an improved developer experience.
\end{itemize}

\subsubsection{Acadaware}
\hfill Lead Web Applications Developer --- \emph{March 2011 - July 2014}

\begin{itemize}
\tightlist{}
\item
  Developed a web application for managing Experiential Education
  programs. Responsibilities included all stages of development, from initial
  requirement gathering to deployment and configuration of a production server
  environment.
\item
  Worked as the sole Full-Stack developer to build and deploy both the front
  and back ends of the application.
\item
  Used the MVC delivery mechanism to structure the web application.
\item
  Designed and implemented a relational database structure suited to the
  application.
\item
  Designed the frontend of the application using modern web technologies such
  as HTML5 and CSS3 while also taking user experience best practices into
  consideration to bring a beautiful and intuitive experience to the user.
\end{itemize}

\subsubsection{Side Projects}

\begin{itemize}
\item
  \href{https://github.com/evanpurkhiser/prolink-go}{github.com/evanpurkhiser/prolink-go},
  \href{https://github.com/evanpurkhiser/prolink-overlay}{github.com/evanpurkhiser/prolink-overlay}

  Proprietary UDP/TCP protocol reversal \& implementation. Websocket
  publishing to React based video stream overlay.
\item
  \href{https://github.com/evanpurkhiser/dots}{github.com/evanpurkhiser/dots}

  Novel `cascading' dot file management solution for sharing personal
  configuration files across systems and platforms.
\end{itemize}

\end{document}
